Details matter: Similar host galaxies can harbor different merging compact binary populations

### 2016-07-12 paper/paper.tex
Adding dwarfs

\newcommand\mc{{\cal M}_c{}}
\newcommand\editremark[1]{{\color{red}#1}}
\newcommand\jillianremark[1]{{\color{blue}#1}}
\newcommand\msun{M_\odot}
\newcommand\unit[1]{\text{#1}}
\newcommand\abbrvPSgrb{PSG}
\newcommand\abbrvPSellipticals{PSE}
\newcommand\abbrvKBLowZa{BD2010}
\newcommand\ForInternalReference[1]{}
\newcommand\modelDefault{A}
\newcommand\modelNiino{A'}
\newcommand\modelKW{D}
\newcommand\modelMannucci{D'}
\newcommand\modelKB{B}
\newcommand\modelPanter{C}
\newcommand\cqg{CQG}
\newcommand\E[1]{\left<#1\right>}
%\newcommand\aap{A\&A}
%\newcommand\apss{APSS}
%\newcommand\aaps{AAPS}
%% \newcommand\apjs{ApJ S}
%% \newcommand\aj{AJ}
%% \newcommand\apjl{ApJL}
%% \newcommand\mnras{MNRAS}
%% \newcommand\pasp{PASP}
%% \newcommand\pasj{PASJ}
%% \newcommand\araa{ARAA}
%% \newcommand\physrep{Phys. Rep.}

@@

\editremark{We will be very careful to specify how SFR and metallicity are measured, backtracking}

Add me: \cite{Kirby13}
Add me but note conflict \cite{Somerville15}, etc

Add me: \citet{Madau14}

@@

\section{Introduction}
% POINT: LIGO soon will detect compact binary mergers....
%     ... and possibly EM counter part too
%     ... which will enable new physics
Gravitational waves have been detected from  coalescing  black hole binaries \citep{DetectionPaper,LIGO-O1-BBH}. 
Over the next few years, ground-based gravitational wave detectors like LIGO 
and Virgo  should detect the gravitational
wave signal from many more similar merging compact binaries \citep{LIGO-O1-BBH,RatesPaper,gwastro-EventPopsynPaper-2016}, as well as  binary  neutron stars and black hole-neutron star binaries \citep{LIGO-Inspiral-Rates,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
%
The host galaxies of gravitational wave sources will be identified, either directly or statistically.  
On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
% People we can't afford the space to cite, alas:
%    - 2015arXiv150101986H   -
%    - 2013MNRAS.430.2121P - Rosswog recent
%    - Shibata group/Koutarou
In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
the sky position and therefore approximate birthplace of each merging binary.    
%
On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \cite{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
networks increase in sensitivity, these localizations will allow statistical and, eventually, unique identification of
host galaxies directly, even without associated electromagnetic emission.
%
As with supernovae and  GRBs, these host galaxy associations   are expected to tightly constrain models for compact binary
formation; see, for comparison,  \citet{2011MNRAS.412.1508M}, \citet{long-grb-GuettaPiran2007},
\citet{2014ARAA..52...43B}, and references therein. %2010ApJ...722.1879M,2010MNRAS.407.1314M}.     
%

% POINT: Huge detail possible
The host galaxies of distant short GRBs have already been extensively investigated, with the associations being used to
draw preliminary conclusions about their progenitors  \cite{2014ARAA..52...43B}.   
%Of necessity, these analyses  on bulk correlations, often stacked to increase significance across multiple sources
%\editremark{clean up/don't piss off   Edo}.  
Unlike GRBs, detected gravitational wave sources will be limited by the range of LIGO to the local universe; for
example,  binary neutron star sources should be closer than $400\unit{Mpc}$.  Due to their proximity, each host galaxy
can be explored at great depth and detail via  position-resolved spectroscopy, enabling detailed position-resolved star-formation
and chemical evolution histories \editremark{citation: need better ones} \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C, Dalcanton09,Williams11,CALIFA}. \jillianremark{Do you want citations of GRB host observations or just general galaxy stuff?}
% POINT: But is it useful?
In this work, we demonstrate by concrete example that detailed analysis of individual galaxies can be essential to
investigate key physical questions about the origin of compact binary mergers.

This paper is organized as follows. 
In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  two galaxies.  Though these two
galaxies are at  present similar to the Milky Way, we
show that their star formation and chemical evolution history have subtle but important differences due to their
distinctive merger histories.   To demonstrate
these differences have a significant practical impact,  in \S \ref{sec:model}, we introduce a simple,
metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to demonstrate the binary black hole coalescence rate
depends sensitively on the galaxy's assembly history, in a manner which is far from apparent from its present-day
properties.  
In \S \ref{sec:results} we show that while these two galaxy formation models should produce comparable detectable binary neutron star
populations, these two scenarios could produce dramatically different populations of electromagnetically detectable
merging black hole-neutron star binaries. 
%

@@

\noindent
where the star formation efficiency parameter $c^*$ is set to 0.1 such
that our galaxies match the observed Kennicutt-Schmidt law
\citep{Kennicutt89};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
particle masses;\footnote{In our high-resolution simulations \textbf{ROS-check!}\jillianremark{this number is correct, is that what you want to check? - JMB}, each gas particle starts with a mass
  $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{Christensen10} for a discussion
of resolution issues in these SPH simulations.} $t_{form}$ is the dynamical time for the gas
particle; and $\Delta t$ is the time between star formation episodes,
which we set to 1 Myr.  We model supernova feedback using the
blastwave formalism described in \citet{McKee77} and implemented in
our simulations as in \citet{Stinson06}.  Each supernova releases
$E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
determined by the blastwave equations.  These particles are not
allowed to cool for the duration of the blastwave, mimicking the
snowplow phase of a supernova explosion.  Previous works have found
that this set of parameters results in realistic galaxies which obey a
number of observed relations such as the mass-metallicity relation
\citep{Brooks07}, the Tully-Fisher relation \citep{Governato09}, and
the size-luminosity relation \citep{Brooks11}, as well as reproduce
the detailed characteristics of bulgeless dwarf galaxies
\citep{Governato10} and the Milky Way \citep{Guedes11}.

@@

{\bf Richard go ahead and edit this however is needed.}  The evolution
of a galaxy, in terms of its stellar mass and metallicity evolution,
depends strongly on its interaction history.  Galaxies which appear
similar at the present day may have had drastically different
histories, which may result in differences in compact object merger
rates.  To investigate whether galaxy history affects the GRB event
rate, we have chosen two simulations which are extremely similar at $z
= 0$ but differ strongly in their merger histories.

The simulation h277 (Boring Galaxy) is a Milky Way analog with a
quiescent merger history.  It experiences its last major merger at $z
= 3$, after which a small number of minor interactions permeate its
life.  This simulation has been shown to emulate several Milky Way
properties, including stellar dynamics
\citep{Loebman12,Loebman14,Kassin14}, baryon fraction
\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir} =
6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
\msun$, and maximum circular velocity $v_{circ} = 235$ km s$^{-1}$.

  The simulation h258 (Exciting Galaxy), on the other hand, has a much
  more active merger history.  At $z = 1$ there is a 1:1 merger event;
  a gas disk rapidly reforms following the collision (see
  \citet{Governato09}), resulting in a massive disk galaxy at $z = 0$
  which looks remarkably similar to the Milky Way and to the other
  simulation, h277.  Prior to the $z = 1$ merger, each of the two
  progenitor galaxies actually experiences its own additional major
  merger events around $z = 2$.  The combination of
  the series of major mergers, plus a number of minor interactions and
  flybys, gives a stark contrast to the relatively quiescent history
  of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}
  \msun$, and maximum circular velocity $v_{circ} = 242$ km s$^{-1}$.  \editremark{Might we want to show the images of these galaxies?}

@@

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/boring}
\includegraphics[width=\columnwidth]{Figures/exciting}
\caption{Synthetic SDSS $gri$ images of our two Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
\label{fig:images}
}
\end{figure*}

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/sfh}
\includegraphics[width=\columnwidth]{Figures/zvst}
\caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
  versus time.  Black corresponds to galaxy A (``boring'') and red to galaxy B (``exciting'').  
\emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
newly-born stars have greater metallicity.  When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
merger of  near the peak of their
star-forming history, newly-born stars are created with significantly different metallicity.  Additionally, prior to the
second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the ``exciting'' galaxy at a systematically lower
metallicity than in the ``boring'' counterpart.
}
\end{figure*}

@@

%\editremark{recheck numbers: we are tweaking things, and Zsun is seemingly inconsistent in the two approaches }
 Our two galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
 times.  
However, at early times, the exciting galaxy forms stars for $\simeq 2\unit{Gyr}$ at a lower characteristic metallicity
($Z\simeq 0.8 \times10^{-3}$) compared
to the boring galaxy ($Z\simeq 2\times 10^{-3}$).  In this reigme, the formation efficiency $\lambda$ and sensitive volume $V$
can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{boring}/(\lambda
V)_{exciting} \simeq 7$.    However, in this same epoch, the star formation rate in the exciting (low-metallicity)
galaxy is smaller, by a factor of roughly 2.
% 1e-3:  V = 276, lambda= 400   
% 2e-3:  V= 152.657625157, lambda = 100
% so the ratio should be a factor of about 7x higher due to this region.
Therefore, though only a fraction \textbf{XXX} of all star formation occurs in this epoch, by this order of magnitude
argument, the overall number of
present-day coalescing binary black holes in our two galaxies is expected to differ by as much as a factor of order \textbf{only
a few percent.}  
%
Using the concrete phenomenological calculations described above, we in fact find
$r_{D,boring}/r_{D,exciting}=\textbf{ZZZ}$.

@@

More broadly, Table \ref{tab:Results} shows the results of our calculations for the three types of compact binaries
described above.   These calculations show just how dramatically different the compact binary populations of galaxies
with similar present-day mass but different star formation histories could be.   In particular, dwarf galaxies have an
exceptionally large fraction of low-metallicity star formation in their history.  The precise details of their chemical
evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
the conservative choices described above for the dependence of rate on metallicity.

@@

\begin{table}
\begin{centering}
\begin{tabular}{|ll|l|}\hline
 \text{Boring} & \text{BHBH} & 1.05 \\
 \text{Exciting} & \text{BHBH} & 1.11 \\
 \text{Dwarf1} & \text{BHBH} & 3.14 \\
 \text{Dwarf2} & \text{BHBH} & 10.3 \\ \hline
 \text{Boring} & \text{NSNS} & 0.000425 \\
 \text{Exciting} & \text{NSNS} & 0.000513 \\ \hline
 \text{Boring} & \text{BHNS} & 0.00162 \\
 \text{Exciting} & \text{BHNS} & 0.00195 \\
 \text{Dwarf1} & \text{BHNS} & 0.00217 \\
 \text{Dwarf2} & \text{BHNS} & 0.00182\\  \hline
\end{tabular}
\end{centering}
\caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
  discussed.  
}
\end{table}

\section{Implications for transient multimessenger astronomy}

@@

\section{Conclusions}

@@

For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate can vary by factors of several in otherwise
similar present-day environments.   Our calculations supports and extends prior investigations which demonstrated both
that black hole merger rates depend sensitively on low-metallicitiy environments
\cite{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}.   More broadly,
because compact binaries can merge long after they form, their host galaxy can evolve substantially in composition
between birth and merger.
%% and that the delay between compact
%% binary formation and coalesence ccn be
%% the sensitive dependence of binary evolution on
%% metallicity implies that
%% * BBH properties far from apparent.  No surprise: delays can be long , particularly because formation in low Z favored,
%% so system changes significantly from assembly conditions

The detailed analysis of the compact binary populations formed through the assembly history of individual galaxies is
complementary to the  population-based approach reported in
\cite{2016arXiv160508783L}.     More broadly, our analysis reflect  similar theoretical studies performed in the interpretation of, for
example, long GRBs and their host galaxies. 
For example, \cite{2009ApJ...702..377K} demonstrated that a sufficiently strong bias towards low-metallicity star formation would predict
most  events in the local universe occur low-mass and dwarf galaxies.
%<
For less extreme metallicity biases, subsequent calculations by  \citet{2011MNRAS.417..567N} demonstrated that the
metallicity distribution within galaxies will usually lead to events in a wide range of host galaxies in the local universe.
% which favored formation in a wide range of galaxies and event times.   % that analysis also
                                % used a poor input from BSE, about the coalescence delay

>>>>

\newcommand\mc{{\cal M}_c{}}
\newcommand\editremark[1]{{\color{red}#1}}
\newcommand\jillianremark[1]{{\color{blue}#1}}
\newcommand\msun{M_\odot}
\newcommand\unit[1]{\text{#1}}
\newcommand\abbrvPSgrb{PSG}
\newcommand\abbrvPSellipticals{PSE}
\newcommand\abbrvKBLowZa{BD2010}
\newcommand\ForInternalReference[1]{}
\newcommand\modelDefault{A}
\newcommand\modelNiino{A'}
\newcommand\modelKW{D}
\newcommand\modelMannucci{D'}
\newcommand\modelKB{B}
\newcommand\modelPanter{C}
\newcommand\cqg{CQG}
\newcommand\ExcitingGalaxy{h258}
\newcommand\BoringGalaxy{h277}
\newcommand\DwarfOne{h603}
\newcommand\DwarfTwo{h516}
\newcommand\DwarfThree{??}
\newcommand\DwarfFour{XX}
\newcommand\MysteryGalaxy{YY}
\newcommand\ControlGalaxy{ZZ}
\newcommand\E[1]{\left<#1\right>}
%\newcommand\aap{A\&A}
%\newcommand\apss{APSS}
%\newcommand\aaps{AAPS}
%% \newcommand\apjs{ApJ S}
%% \newcommand\aj{AJ}
%% \newcommand\apjl{ApJL}
%% \newcommand\mnras{MNRAS}
%% \newcommand\pasp{PASP}
%% \newcommand\pasj{PASJ}
%% \newcommand\araa{ARAA}
%% \newcommand\physrep{Phys. Rep.}

@@

%\editremark{We will be very careful to specify how SFR and metallicity are measured, backtracking}

%Add me: \cite{Kirby13}
\editremark{Jillian}: Add me but note conflict \cite{Somerville15}, etc or \cite{2015ARAA..53...51S}

%Add me: \citet{Madau14}  % not necessary, we are not doing a synthetic universe

@@

\section{Introduction}
% POINT: LIGO soon will detect compact binary mergers....
%     ... and possibly EM counter part too
%     ... which will enable new physics
Gravitational waves have been detected from  coalescing  black hole binaries \citep{DetectionPaper,LIGO-O1-BBH}. 
Over the next few years, ground-based gravitational wave detectors like LIGO 
and Virgo  should detect the gravitational
wave signal from many more similar merging compact binaries \citep{LIGO-O1-BBH,RatesPaper,gwastro-EventPopsynPaper-2016}, as well as  binary  neutron stars and black hole-neutron star binaries \citep{LIGO-Inspiral-Rates,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.
%
The host galaxies of gravitational wave sources will be identified, either directly or statistically.  
On the one hand, addition to the strong gravitational wave signal, mergers of neutron stars are expected to  frequently be accompanied by detectable
electromagnetic radiation  via a number of  mechanisms, including a strong but tightly beamed
ultrarelativistic jet and weakly-beamed but more isotropic thermal radiation from an expanding hot shell
\citep[see,e.g.,][and references therein]{2013PhRvL.111r1101C,short-grb-GWCoincidenceEM-MetzgerBerger2011}.  
% People we can't afford the space to cite, alas:
%    - 2015arXiv150101986H   -
%    - 2013MNRAS.430.2121P - Rosswog recent
%    - Shibata group/Koutarou
In addition to providing a wealth of information about the merger event itself, a multimessenger detection will pin down
the sky position and therefore approximate birthplace of each merging binary.    
%
On the other hand, gravitational wave detectors can perform high-precision sky and volumetric localization \citep{2016LRR....19....1A,2016arXiv160307333S}.  As GW detector
networks increase in sensitivity, these localizations will allow statistical and, eventually, unique identification of
host galaxies directly, even without associated electromagnetic emission.
%
As with supernovae and  GRBs, these host galaxy associations   are expected to tightly constrain models for compact binary
formation; see, for comparison,  \citet{2011MNRAS.412.1508M}, \citet{long-grb-GuettaPiran2007},
\citet{2014ARAA..52...43B}, and references therein. %2010ApJ...722.1879M,2010MNRAS.407.1314M}.     
%

% POINT: Huge detail possible
The host galaxies of distant short GRBs have already been extensively investigated, with the associations being used to
draw preliminary conclusions about their progenitors  \citep{2014ARAA..52...43B}.   
%Of necessity, these analyses  on bulk correlations, often stacked to increase significance across multiple sources
%\editremark{clean up/don't piss off   Edo}.  
Unlike GRBs, detected gravitational wave sources will be limited by the range of LIGO to the local universe; for
example,  binary neutron star sources should be closer than $400\unit{Mpc}$.  Due to their proximity, each host galaxy
can be explored at great depth and detail via  position-resolved spectroscopy, enabling detailed position-resolved star-formation
and chemical evolution histories  \citep[see,e.g.][]{2009MNRAS.396..462K,2014MNRAS.444..336C,
  Dalcanton09,Williams11,CALIFA}.  
% POINT: But is it useful?
In this work, we demonstrate by concrete example that detailed analysis of individual galaxies can be essential to
investigate key physical questions about the origin of compact binary mergers.

This paper is organized as follows. 
In \S \ref{sec:sims}, we describe detailed hydrodynamical simulations of  two galaxies.  Though these two
galaxies are at  present similar to the Milky Way, we
show that their star formation and chemical evolution history have subtle but important differences due to their
distinctive merger histories.   To demonstrate
these differences have a significant practical impact,  in \S \ref{sec:model}, we introduce a simple,
metallicity-dependent  phenomenological model to calculate the present-day rate and mass distribution of compact binary
mergers from  a galaxy's known history.   In \S \ref{sec:results:BBH}, we use this model to demonstrate the binary black
hole (BH-BH) coalescence rate
can depend sensitively on the galaxy's assembly history, in a manner which is far from apparent from its present-day
properties.    We also demonstrate that even the coalescence rates of binary neutron stars (NSNS) and black hole-neutron
star (BH-NS) binaries also depend surprisingly sensitively on the assembly history of each galaxy. 
In \S~\ref{sec:Discussion} we discuss the implications of our study for the interpretation of host galaxy associations
identified via transient multmiessenger astronomy, in the short and long term.  We summarize our results in \S~ \ref{sec:conclude}.
%% In \S \ref{sec:results} we show that while these two galaxy formation models should produce comparable detectable binary neutron star
%% populations, these two scenarios could produce dramatically different populations of electromagnetically detectable
%% merging black hole-neutron star binaries. 
%

@@

\noindent
where the star formation efficiency parameter $c^*$ is set to 0.1 such
that our galaxies match the observed Kennicutt-Schmidt law
\citep{Kennicutt89};  X$_{\rm H_2}$ is the molecular hydrogen fraction of the gas particle; $m_{star}$ and $m_{gas}$ are the star and gas
particle masses;\footnote{In our high-resolution simulations, each gas particle starts with a mass
  $m_{gas,0}=26,676 M_\odot$, gaining mass from feedback and losing it to star formation.  Each star particle, when
  formed, has $1/3$ of the progenitor mass of the forming gas particle.  See \cite{Christensen10} for a discussion
of resolution issues in these SPH simulations.} $t_{form}$ is the dynamical time for the gas
particle; and $\Delta t$ is the time between star formation episodes,
which we set to 1 Myr.  We model supernova feedback using the
blastwave formalism described in \citet{McKee77} and implemented in
our simulations as in \citet{Stinson06}.  Each supernova releases
$E_{SN} = 10^{51}$ erg into the surrounding gas with a radius
determined by the blastwave equations.  These particles are not
allowed to cool for the duration of the blastwave, mimicking the
snowplow phase of a supernova explosion.  Previous works have found
that this set of parameters results in realistic galaxies which obey a
number of observed relations such as the mass-metallicity relation
\citep{Brooks07,Kirby13}, the Tully-Fisher relation \citep{Governato09}, and
the size-luminosity relation \citep{Brooks11}, as well as reproduce
the detailed characteristics of bulgeless dwarf galaxies
\citep{Governato10} and the Milky Way \citep{Guedes11}.

@@

%{\bf Richard go ahead and edit this however is needed.}  
The evolution
of a galaxy, in terms of its stellar mass and metallicity evolution,
depends strongly on its interaction history.  Galaxies which appear
similar at the present day may have had drastically different
histories, which may result in differences in compact object merger
rates.  To investigate whether galaxy history affects the GRB event
rate, we have chosen two simulations which are extremely similar at $z
= 0$ but differ strongly in their merger histories; see Figure \ref{fig:GalaxyImages}.

The simulation h277  is a Milky Way analog with a
quiescent merger history.  It experiences its last major merger at $z
= 3$, after which a small number of minor interactions permeate its
life.  This simulation has been shown to emulate several Milky Way
properties, including stellar dynamics
\citep{Loebman12,Loebman14,Kassin14}, baryon fraction
\citep{Munshi13}, halo properties \citep{Zolotov09,Zolotov10}, and
disk properties \citep{Brooks11}.  It has a virial mass of $M_{vir} =
6.79 \times 10^{11} \msun$, stellar mass $M_* = 4.24 \times 10^{10}
\msun$, and maximum circular velocity $v_{circ} = 235$ km s$^{-1}$.

  The simulation h258 (Exciting Galaxy), on the other hand, has a much
  more active merger history.  At $z = 1$ there is a 1:1 merger event;
  a gas disk rapidly reforms following the collision (see
  \citet{Governato09}), resulting in a massive disk galaxy at $z = 0$
  which looks remarkably similar to the Milky Way and to the other
  simulation, h277.  Prior to the $z = 1$ merger, each of the two
  progenitor galaxies actually experiences its own additional major
  merger events around $z = 2$.  The combination of
  the series of major mergers, plus a number of minor interactions and
  flybys, gives a stark contrast to the relatively quiescent history
  of h277.  At $z = 0$, h258 has a virial mass of $M_{vir} = 7.74
  \times 10^{11} \msun$, stellar mass $M_* = 4.46 \times 10^{10}
  \msun$, and maximum circular velocity $v_{circ} = 242$ km s$^{-1}$.  %\editremark{Might we want to show the images of these galaxies?}

@@

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/boring}
\includegraphics[width=\columnwidth]{Figures/exciting}
\caption{\label{fig:GalaxyImages}Synthetic SDSS $gri$ images of our two Milky Way-type galaxies, h277 (left) and h258 (right), created with \textsc{SUNRISE} \citep{Jonsson06}.
\label{fig:images}
}
\end{figure*}

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/sfh}
\includegraphics[width=\columnwidth]{Figures/zvst}
\caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
  versus time.  Black corresponds to \BoringGalaxy{} and red to \ExcitingGalaxy.  
\emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
newly-born stars have greater metallicity.  When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
merger of  near the peak of their
star-forming history, newly-born stars are created with significantly different metallicity.  Additionally, prior to the
second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the \ExcitingGalaxy{} galaxy at a systematically lower
metallicity than in the \BoringGalaxy{} counterpart.
}
\end{figure*}

\subsection{Dwarf galaxies}

We have also employed the results of detailed simulations for several dwarf galaxies: \DwarfOne{}, \DwarfTwo{}, and others.

%% h516 = dwarf2
%% h603 = dwarf1
%% dwarf3 = h799
%% mystery = ? 
%% control =?

@@

%\editremark{recheck numbers: we are tweaking things, and Zsun is seemingly inconsistent in the two approaches }
 Our two galaxies have extremely similar star formation histories and metallicity evolution, particularly at late
 times.  
However, at early times, the \ExcitingGalaxy{} galaxy forms stars for $\simeq 2\unit{Gyr}$ at a lower characteristic metallicity
($Z\simeq 0.8 \times10^{-3}$) compared
to the \BoringGalaxy{} galaxy ($Z\simeq 2\times 10^{-3}$).  In this reigme, the formation efficiency $\lambda$ and sensitive volume $V$
can depend sensitively on mass; for example, for binary black holes, the ratio of  $(\lambda V)_{\BoringGalaxy{}}/(\lambda
V)_{\ExcitingGalaxy{}} \simeq 7$.    However, in this same epoch, the star formation rate in the \ExcitingGalaxy{} (low-metallicity)
galaxy is smaller, by a factor of roughly 2.
% 1e-3:  V = 276, lambda= 400   
% 2e-3:  V= 152.657625157, lambda = 100
% so the ratio should be a factor of about 7x higher due to this region.
Therefore, though only a fraction \textbf{XXX} of all star formation occurs in this epoch, by this order of magnitude
argument, the overall number of
present-day coalescing binary black holes in our two galaxies is expected to differ by as much as a factor of order \textbf{only
a few percent.}  
%
Using the concrete phenomenological calculations described above, we in fact find
$r_{D,\BoringGalaxy{}}/r_{D,\ExcitingGalaxy{}}=\textbf{ZZZ}$.

@@

More broadly, Table \ref{tab:Results} shows the results of our calculations for the three types of compact binaries
described above.   These calculations show just how dramatically different the compact binary populations of galaxies
with similar present-day mass but different star formation histories could be.   In particular, dwarf galaxies have an
exceptionally large fraction of low-metallicity star formation in their history \cite{Kirby13}.  The precise details of their chemical
evolution can modify their present-day binary black hole binary populations by factors of order a few, despite  adopting
the conservative choices described above for the dependence of rate on metallicity.

@@

\begin{table}
\begin{centering}
\begin{tabular}{|ll|l|}\hline
 \text{\BoringGalaxy{}} & \text{BHBH} & 1.05 \\
 \text{\ExcitingGalaxy{}} & \text{BHBH} & 1.11 \\
 \text{\DwarfOne} & \text{BHBH} & 3.14 \\
 \text{\DwarfTwo} & \text{BHBH} & 10.3 \\ \hline
 \text{\BoringGalaxy{}} & \text{NSNS} & 0.000425 \\
 \text{\ExcitingGalaxy{}} & \text{NSNS} & 0.000513 \\ \hline
 \text{\BoringGalaxy{}} & \text{BHNS} & 0.00162 \\
 \text{\ExcitingGalaxy{}} & \text{BHNS} & 0.00195 \\
 \text{\DwarfOne} & \text{BHNS} & 0.00217 \\
 \text{\DwarfTwo} & \text{BHNS} & 0.00182\\  \hline
\end{tabular}
\end{centering}
\caption{\label{tab:Results}\textbf{Event rates per unit mass $r_D/M$, arbitrary units}, for the three different types of binaries
  discussed.  
}
\end{table}

\section{Implications for transient multimessenger astronomy}
\label{sec:Discussion}

@@

\section{Conclusions}
\label{sec:conclude}

@@

For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate can vary by factors of several in otherwise
similar present-day environments.   Our calculations support and extend prior investigations which demonstrated both
that black hole merger rates depend sensitively on low-metallicitiy environments
\citep[see,e.g.][]{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}.   More broadly,
because compact binaries can merge long after they form, their host galaxy can evolve substantially in composition
between birth and merger.
%% and that the delay between compact
%% binary formation and coalesence ccn be
%% the sensitive dependence of binary evolution on
%% metallicity implies that
%% * BBH properties far from apparent.  No surprise: delays can be long , particularly because formation in low Z favored,
%% so system changes significantly from assembly conditions

The detailed analysis of the compact binary populations formed through the assembly history of individual galaxies is
complementary to the  population-based approach reported in
\cite{2016arXiv160508783L}.     More broadly, our analysis reflects  similar theoretical studies performed in the interpretation of, for
example, long GRBs and their host galaxies. 
For example, \cite{2009ApJ...702..377K} demonstrated that a sufficiently strong bias towards low-metallicity star formation would predict
most  events in the local universe occur low-mass and dwarf galaxies.
%<
For less extreme metallicity biases, subsequent calculations by  \citet{2011MNRAS.417..567N} demonstrated that the
metallicity distribution within galaxies will usually lead to events in a wide range of host galaxies in the local universe.
% which favored formation in a wide range of galaxies and event times.   % that analysis also
                                % used a poor input from BSE, about the coalescence delay
